Contracts for unions and intersections are hard for Nickel

### 2021-05-20 paper.tex
Smallfixes + review of section 5

Intersections are less prevalent. An intersection is a value that belongs to to
two types at the same time. A simple example is a number literal \nickel{1}
which could be accepted as both an \nickel{Int} and a \nickel{Float} without
having to perform conversions(Figure~\ref{fig:intersection-subytping-ex}). In
this example, the intersection \nickel{Int & Float} plays the role of a subtype
of both \nickel{Int} and \nickel{Float}.

@@

For instance, if the value \nickel{V} is contracted with
\nickel{A /\\ (B \\/ C)}, then, before the contract is checked,
the contract gets opened up to something equivalent to
\nickel{(A /\\ B) \\/ (A /\\ C)}.

This straightforward solutions makes composing the Keil and Thiemann
system with other existing systems more difficult; in the words
of Williams, Morris, and Wadler:
"(...) the monitoring semantics for contracts of intersection and union types given by Keil
and Thiemann are not uniform. (...) If uniformity helps composition, then
special cases can hinder composition."\cite{RootCauseOfBlame}

@@

We see two problems here, a minor one is the fact that two different
semantics need to be defined, which translates either to a difficult
to implement or a difficult to understand system.
A second, major one,
is the dependency added over the evaluation context, since, again,
it makes composing this, with other features desired on programming languages,
difficult, or even impossible (as the case with common subexpression elimination).

@@

$$ K \in \llbracket A \cap B \rrbracket^- ~ if ~ K \in \llbracket A \rrbracket^- \lor K \in \llbracket B \rrbracket^- $$

@@

% K ::= Id | K ◦ □ N | K ◦ V □ | K ◦ □ @pA
\unsure{Is it worth mentioning how continuations are formed?
Should we go so techincal?}

@@

Even worst, the \racket{or/c} contract doesn't allow to have multiple higher order
contracts that could (potentially) apply to a function, these have to be
differentiated by first order markers.
For instance, the code on Figure \ref{code:racket:or/c:working}
would correctly allow only to call
\racket{united} with a \racket{number?},
and it can make this distinction since it knows that
\racket{(lambda (x) x)} can not be a function that takes 2 parameters.
However, the code on Figure \ref{code:racket:or/c:non-working} would fail
before running, since the \racket{or/c} contract is unable to know
which of the two function contracts to use.
Ideally, this last example should just behave as wrapping
the function with the \racket{(-> even? even?)} contract.

>>>>

Intersections are less prevalent. An intersection is a value that belongs to to
two types at the same time. A simple example is a number literal \nickel{1}
which could be accepted as both an \nickel{Int} and a \nickel{Float} without
having to perform conversions(Figure~\ref{fig:intersection-subytping-ex}). In
this example, the intersection \nickel{Int & Float} can be used as a subtype of
both \nickel{Int} and \nickel{Float}.

@@

For instance, if the value \nickel{V} is contracted\todo{(Yann) Contracted means
something else I think} with
\nickel{A & (B | C)}, then, before the contract is checked,
the contract gets opened up to something equivalent to
\nickel{(A & B) | (A & C)}.

This straightforward solutions makes composing the Keil and Thiemann
system with other existing systems more difficult; in the words
of Williams, Morris, and Wadler:
"(\ldots) the monitoring semantics for contracts of intersection and union types given by Keil
and Thiemann are not uniform. (\ldots) If uniformity helps composition, then
special cases can hinder composition."\cite{RootCauseOfBlame}\info{(Yann) Does
it also make it less efficient? If $(A \& B)$ fails because of $B$, their
development causes to recheck the contract $A$ that has been duplicated?}

@@

We see two problems here, a minor one is the fact that two different
semantics need to be defined, which translates either to a difficult
to implement or a difficult to understand system\unsure{(Yann) Is it really a
    problem per se? It is common thing to do (a nice declarative system
    for proofs and an algorithmic one for implementation, proved equivalent).
    Maybe the point is that the algorithmic system is way more complex than the
declarative one}.
A second, major one,
is the dependency added over the evaluation context, since, again,
it makes composing this, with other features desired on programming languages,
difficult, or even impossible (as the case with common subexpression
elimination)\unsure{(Yann) I think we need to substantiate this claim. If this
context dependency explains why CSE is invalid, maybe have a little example?}
\todo{(Yann) TODO: see if there's a low hanging complexity
    argument we can make (like it's quadratic in the number of open contracts or
whatever)}.

@@

$$ K \in \llbracket A \cap B \rrbracket^-~if~K \in \llbracket A \rrbracket^- \lor K \in \llbracket B \rrbracket^- $$

@@

% K ::= Id | K ◦ □ N | K ◦ V □ | K ◦ □ @pA
\unsure{Is it worth mentioning how continuations are formed?
Should we go so techincal?}
\todo{(Yann) Maybe adding a concrete example of this (it can be the same term but with
    concrete types like Number and String and simple contexts like application
to a dumb argument) is sufficient to make the point}

@@

Even worst, the \racket{or/c} contract doesn't allow to have multiple higher order
contracts that could (potentially) apply to a function, these have to be
differentiated by first order markers.
For instance, the code on Figure~\ref{code:racket:or/c:working}
would correctly allow only to call
\racket{united} with a \racket{number?},
and it can make this distinction since it knows that
\racket{(lambda (x) x)} can not be a function that takes 2 parameters.
However, the code on Figure~\ref{code:racket:or/c:non-working} would fail
before running, since the \racket{or/c} contract is unable to know
which of the two function contracts to use.
Ideally, this last example should just behave as wrapping
the function with the \racket{(-> even? even?)} contract.
